Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-02 icse/paper.tex
Paper stuff

\title{Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

@@

@@

\section{CloneRefactor}
The tool: Detect Clones -> Map Context -> Refactor.

@@

\subsubsection{The cyclic nature of refactoring}
Explain how refactoring code clones might open up new refactoring opportunities.

@@

\subsection{Clone context}
How many clones are there in certain contexts?

@@

\subsection{Thresholds}
I think the ultimate goal with this thesis is to experiment the refactored source code

\section{Discussion}

>>>>

\title{Improving Software Maintainability through Automated Refactoring of Code Clones}

@@

\section{Introduction}

@@

\subsection{Code clone definitions}
Quick overview of clone type definitions

@@

\section{CloneRefactor}
The tool: Detect Clones, Map Context, Refactor.

@@

\subsubsection{The cyclic nature of refactoring}
Explain how refactoring code clones might open up new refactoring opportunities. We refactor a project until there are no more open refactoring opportunities.

@@

\subsection{Clone context}
How many clones are there in certain contexts? Experiments for relation, location and context.

@@

\subsection{Thresholds}
I think the ultimate goal with this thesis is to do experiments with different clone thresholds. Which thresholds give clones that we should refactor? For this, we will measure the maintainability of the refactored source code over different thresholds. These thresholds range from minimum clone size, variability and gap size.

\section{Discussion}
\subsection{Clone Definitions}

\subsection{CloneRefactor}

\subsection{Experimental setup}
